---
title: "Simple document"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r round(mean(samp),2)`.

# Section 3

This is going to make a plot! First, I generate a dataframe, than use `ggplot` to make a scatterplot.

```{r chunk_scatter, echo = FALSE}
plot_df = 
  tibble(
    x = rnorm(n = 1000),
    y = 1 + 2 * x + rnorm(n = 1000)
  )

ggplot(plot_df, aes (x = x, y = y)) + geom_point()
```

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

```{r}
learn_assess = 
  tibble(
    norm_samp = rnorm(n = 500, mean = 1),
    norm_samp_pos = norm_samp > 0,
    abs_norm_samp = abs(norm_samp)
  )

ggplot(learn_assess, aes(x=abs_norm_samp)) + geom_histogram()
```

# Section
## Subsection
### Sub-sub section

Here's a list:

* Item 1
* Item 2

